Trends of SDR in Thessaloniki 

### 2022-10-09 Article.Rmd
Commit 2022-10-10 00:17

@@

@@

@@

## Data description

...... Measurements CHP1 CM21

## Data process

We take some steps in order to make the measurements comparable throughout
the dataset. 
<!-- 1au -->
We adjusted all measurements to the mean distance between Sun and Earth.
<!-- TSI -->
And, we make all measurements relative to the .........TSI.......... , 
using an homogenized timeseries of satellite TSI data...........

<!-- Clear Sky -->
We using two selection of our measurements dataset, one with all sky conditions (ALL),
consisting of the whole available data, and one filtered for 'clear sky' 
conditions (CS). The latter was created, using a method adapted to our 
site, and was proposed by @Long2000 and by @Reno2016.

@@

## SZA trends

## Trends consistency

>>>>

goal

basic consepts

@@

## Data process.

To make the measurements comparable throughout the dataset. 
<!-- 1au -->
We adjusted all values to the mean Sun and Earth distance.
<!-- TSI -->
And, we made all measurements relative to the TSI at 1au,
in order to compensate for the the Suns intensity variability,
using an homogenized timeseries of satellite TSI observations.
As a result, we processed all radiation data as a fraction of Suns TSI.

<!-- Clear Sky -->
For this analysis, we need .............
, we using two selection of our measurements dataset, one with all sky conditions (ALL),
consisting of the whole available data, and one filtered for 'clear sky' 
conditions (CS). The latter was created, using a method adapted to our 
site, and was proposed by @Long2000 and by @Reno2016.

@@

## Long term trends

## Zenith angle dependance and years seasons.

## Consistency of the trends

@@

@@
